Git Learning Notes

### 2014-10-24 ch-wox/ch-wox.tex
figure caption fixed, proof reading and introduction chapter done

Metallic tungsten powders were utilized as source materials in this work. Four kinds of W powder were used in total, as summarized in Table.~\ref{tab:powder}. Two growth configurations were explored, namely ordinary transport and seeded growth.
% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{Tungsten powders size and purity}\label{tab:powder}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
\bottomrule
\end{tabular}
\end{table}

In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed. The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side. The cleaning procedures have been elucidated on page.~\pageref{ch2sub}. The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 in.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 sccm \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{CVD_and_temp.jpg}
\caption[\ce{WO3} NW growth: OT]{Chemical vapor system and its temperature profile. The nominal NWs growth temperature were estimated according to the interpolation data. The zero inch location is defined at the upstream edge of furnace.}
\label{fig:wogrow}
\end{figure}

@@

The change of metallic W source after growth carries important information on the growth. So before examining the deposition on substrates, the SEM images of all powders before and after growth are presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
% powder before growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_before.jpg}
\caption[SEM images of W powder before growth]{SEM images of W powder before growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N, respectively.}
\label{fig:pdbefore}
\end{figure}
Tungsten metal crystallizes in body center cubic (BCC) phase. Overall, the facets were still discernible. The 4N5 and 5N powders share similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d). In contrast, 3N powders are almost half the size of 3N5 ones, and have more uniform size distribution as well. Absolute size and its distribution play a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
% powder after growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_after.jpg}
\caption[SEM images of W powder after growth]{SEM images of W powder after growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdafter}
\end{figure}
After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both develop the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) become bundled rods. This difference mainly arises from the average size, which will dictate the degree of oxidation. Another possible reason is the presence of foreign elements in each W powders. As indicated by the certificate of analysis from corresponding vendors (attached in Appendix), carbon, nickel, iron and sodium can amount up to tens of ppm in low purity W sources.

The sodium contents in 3N powders fundamentally change the deposition in ordinary transport growth. Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a. The nanostructures were \glspl{nw} with lengths up to several hundred microns and diameters about 40 to 500 nm. The deposition of nanowires was generally located on the substrates with the growth temperature ranging from 660 to 420 \si{\degreeCelsius}. Enlarged view at higher magnification revealed some nanowires were cylindrical and some were bundled belt. Rectangular microplate structures grew at lower temperature end of substrate, as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset. The chemical compositions of the deposition were analyzed using \gls{edx}. A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate. The crystal structures of the as-synthesized specimens were examined using XRD. The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d. The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \AA, \emph{b}=7.2911 \AA, \emph{c}=18.5510 \AA, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \AA, \emph{b}=3.8940 \AA, \emph{c}=8.2550 \AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$). The tungsten oxide is the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$).

% nawox sem edx
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on SiO2-Si substrate and (b) rectangular microplates grow among the nanowires. (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
\label{fig:nawoxsemedx}
\end{figure}

XRD measurements revealed the overall structure of the specimen. To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and \gls{edx} were performed on more than 20 nanowires. The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase (Fig.~\ref{fig:nawoxtem}a-c). The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire exhibits a single-crystalline structure. The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}b was recorded in $[\bar{1}10]$ axis. Based on the analyses on a series of diffraction patterns and HRTEM images, the nanowire was confirmed as the triclinic \ce{Na5W_{14}O_{44}}. The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane. EDX measurement (Fig.~\ref{fig:nawoxtem}c) shows the nanowire consisted of W, Na, and O. No other elements were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase (Fig.~\ref{fig:nawoxtem}d-f). The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone. The growth direction of the \ce{WO3} nanowire was determined to be perpendicular to the (002) plane with a d-spacing of 0.38 nm. EDX spectrum in Fig.~\ref{fig:nawoxtem}f shows the nanowire consisted of W and O without Na or other impurities. The rectangular microplate structures shown in Fig.~\ref{fig:nawoxsemedx}b were also collected for TEM examination. These microplate structures were identified to be the triclinic \ce{Na2W4O_{13}} phase. The SAED in Fig.~\ref{fig:nawoxtem}h was recorded in [101] axis. No high-quality HRTEM images were acquired for the \ce{Na2W4O_{13}} plate due to its thickness. The long edge of the plate was identified as parallel to the (010) plane and the short edge parallel to the ($\bar{1}01$) plane. From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis ([001]) and the short edge is along the $\vec{b}$ axis ([010]). Fig.~\ref{fig:nawoxtem}i shows the plate structure also consisted of W, Na, and O and no other impurities were detected. Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c. This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of these two phases.
% tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_tem.jpg}
\caption[SEM images of morphology evolution]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i). }
\label{fig:nawoxtem}
\end{figure}

Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires. Fig.~\ref{fig:nawoxram}a shows the m-Raman spectrum of the microplates. The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b. The spectrum shows major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions. As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consist of only little or no amount of \ce{WO3} and \ce{Na2W4O_{13}} phases. Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures. According to XRD and TEM analyses, the nanowires are mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase. So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
% nawox raman
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_raman_series}
\caption[Raman spectra on \ce{Na_xWO3}]{Micro-Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
\label{fig:nawoxram}
\end{figure}
Based on the correlation of Raman spectra and crystallographic data of a variety of tungsten bronze, an empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths has been found as
\begin{equation}\label{eq:wobond}
\nu = 25823 \exp(-1.902\cdot R)
\end{equation}
where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \si{\angstrom}. The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}. Multi-peak Lorentzian fitting is preformed to precisely determine the central maximum. Good fitting is obtained as shown in Fig.~\ref{fig:naworamfit}. The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} are then listed in Table~\ref{tab:nawobond}. The predicted \ce{W-O} bond lengths agree very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak probably is caused by \ce{Na-O} bond.
% Na5 raman fitting
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peak Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}. The peaks sum height difference is caused by different baseline value adopted in each fitting.}
\label{fig:naworamfit}
\end{figure}

@@

Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na. The sodium concentration in 3N source was 20 ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively. To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N). These ultra-high purity W sources produced pure tungsten oxide deposition and no Na content was detected by EDX. These results verified the Na content was mainly from the 3N W powders. In the OT growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors. The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item only small amount of the tungsten source was consumed during the growth; and
\item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source is difficult to probe. However, the evaporation rate of the Na content is expected to be high when heated at 1000 \si{\degreeCelsius}. This assumption is supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source. Put it in another way, this means that the majority of Na content was already evaporated in previous experiment. Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_edx_series.jpg}
\caption[Photograph of a series of 3N growth]{(a) Photograph of a series of specimens grown in the same reaction chamber with the increase of growth number showing different growth zones and corresponding morphology changes. (b) Change of Na/W ratios with the increase of growth number at different growth zones.}
\label{fig:nawoxser}
\end{figure}

As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth number. Three growth zones of nanowires can be identified on basis of the coverage and density of the nanowires, as delimited by the vertical guide line. The growth Zone I was located at high temperature end ranging from 660 to 520 \si{\degreeCelsius}, Zone II was from 520 to 470 \si{\degreeCelsius}, and Zone III from 470 to 420 \si{\degreeCelsius}. Detailed morphological changes are depicted in Fig.~\ref{fig:nawoxsemall}.
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_sem_series.jpg}
\caption[SEM images of morphology evolution]{Low magnification SEM images of the NWs at different growth zones showing morphology changes with the increase of growth number. The insets show detailed structures of the NWs.}
\label{fig:nawoxsemall}
\end{figure}
For the first growth (Fig.~\ref{fig:nawoxsemall}a-c) in a new clean reaction chamber, there were only a little nanowires scattered in Zone I (Fig.~\ref{fig:nawoxsemall}a), ultra-long nanowires were mostly found in Zone II with higher density and coverage (Fig.~\ref{fig:nawoxsemall}b), and in Zone III the coverage, density, and length of nanowires gradually reduced as the growth location moved downstream (Fig.~\ref{fig:nawoxsemall}c). With growth number increased to 3 (Fig.~\ref{fig:nawoxsemall}d-f) and 5 (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones. Zone I saw the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g. After the fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones. For Zones I and II, no significant morphology change was observed with further increase of the growth number up to 8. However, for Zone III the microplate structures (shown in inset of Fig.~\ref{fig:nawoxsemall}i) kept increasing significantly with the growth number. EDX study revealed the variation of Na concentration in the deposition with the growth number. Fig.~\ref{fig:nawoxser}b shows the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones. Generally, the Na/W ratios at all growth zones increased with the increase of growth number. The large fluctuation of Na/W ratio at Zone III was presumably due to the uneven distribution of Na content with different morphologies at Zone III.

@@

\subsection{Tungsten Oxides: Seeded Growth }\label{sec:sgfg}

>>>>

Metallic tungsten powders were utilized as source materials in this work. Four kinds of W powder were used in total, as summarized in Table~\ref{tab:powder}. Two growth configurations were explored, namely ordinary transport and seeded growth.
% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{Tungsten powders size and purity}\label{tab:powder}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
\bottomrule
\end{tabular}
\end{table}

In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed. The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side. The cleaning procedures have been elucidated on page.~\pageref{ch2sub}. The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{CVD_and_temp.jpg}
\caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile. The nominal NWs growth temperature were estimated according to the interpolation data. Zero inch location is defined at the upstream edge of furnace.}
\label{fig:wogrow}
\end{figure}

@@

The change of metallic W source after growth carries important information on the growth. So before examining the deposition on substrates, the SEM images of all powders before and after growth are presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
% powder before growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_before.jpg}
\caption[SEM images of W powder before growth]{SEM images of W powder before growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N, respectively.}
\label{fig:pdbefore}
\end{figure}
Tungsten metal crystallizes in body center cubic (BCC) phase. Overall, the facets were still discernible. The 4N5 and 5N powders share similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d). In contrast, 3N powders are almost half the size of 3N5 ones, and have more uniform size distribution as well. Absolute size and its distribution play a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
% powder after growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_after.jpg}
\caption[SEM images of W powder after growth]{SEM images of W powder after growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdafter}
\end{figure}
After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both develop the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) become bundled rods. This difference mainly arises from the average size, which will dictate the degree of oxidation. Another possible reason is the presence of foreign elements in each W powders. As indicated by the certificate of analysis from corresponding vendors, carbon, nickel, iron and sodium can amount up to tens of ppm in low purity W sources.

The sodium contents in 3N powders fundamentally change the deposition in ordinary transport growth. Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a. The nanostructures were \glspl{nw} with lengths up to several hundred microns and diameters about 40 to 500 nm. The deposition of nanowires was generally located on the substrates with the growth temperature ranging from 660 to 420 \si{\degreeCelsius}. Enlarged view at higher magnification revealed some nanowires were cylindrical and some were bundled belt. Rectangular microplate structures grew at lower temperature end of substrate, as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset. The chemical compositions of the deposition were analyzed using \gls{edx}. A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate. The crystal structures of the as-synthesized specimens were examined using XRD. The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d. The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \si{\angstrom}, \emph{b}=7.2911 \si{\angstrom}, \emph{c}=18.5510 \si{\angstrom}, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \si{\angstrom}, \emph{b}=3.8940 \si{\angstrom}, \emph{c}=8.2550 \si{\angstrom}, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$). The tungsten oxide is the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \si{\angstrom}, \emph{b}=7.53889 \si{\angstrom}, \emph{c}=7.6896 \si{\angstrom}, $\beta$=90.89$^\circ$).

% nawox sem edx
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires. (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
\label{fig:nawoxsemedx}
\end{figure}

XRD measurements revealed the overall structure of the specimen. To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and \gls{edx} were performed on more than 20 nanowires. The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase (Fig.~\ref{fig:nawoxtem}a-c). The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire exhibits a single-crystalline structure. The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}b was recorded in $[\bar{1}10]$ axis. Based on the analyses on a series of diffraction patterns and HRTEM images, the nanowire was confirmed as the triclinic \ce{Na5W_{14}O_{44}}. The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane. EDX measurement (Fig.~\ref{fig:nawoxtem}c) shows the nanowire consisted of W, Na, and O. No other elements were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase (Fig.~\ref{fig:nawoxtem}d-f). The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone. The growth direction of the \ce{WO3} nanowire was determined to be perpendicular to the (002) plane with a d-spacing of 0.38 nm. EDX spectrum in Fig.~\ref{fig:nawoxtem}f shows the nanowire consisted of W and O without Na or other impurities. The rectangular microplate structures shown in Fig.~\ref{fig:nawoxsemedx}b were also collected for TEM examination. These microplate structures were identified to be the triclinic \ce{Na2W4O_{13}} phase. The SAED in Fig.~\ref{fig:nawoxtem}h was recorded in [101] axis. No high-quality HRTEM images were acquired for the \ce{Na2W4O_{13}} plate due to its thickness. The long edge of the plate was identified as parallel to the (010) plane and the short edge parallel to the ($\bar{1}01$) plane. From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis and the short edge is along the $\vec{b}$ axis. Fig.~\ref{fig:nawoxtem}i shows the plate structure also consisted of W, Na, and O and no other impurities were detected. Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c. This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of these two phases.
% tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_tem.jpg}
\caption[TEM analyses on sodium tungsten oxide sample]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i).}
\label{fig:nawoxtem}
\end{figure}

Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires. Fig.~\ref{fig:nawoxram}a shows the m-Raman spectrum of the microplates. The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b. The spectrum shows major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions. As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consist of only little or no amount of \ce{WO3} and \ce{Na2W4O_{13}} phases. Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures. According to XRD and TEM analyses, the nanowires are mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase. So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
% nawox raman
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_raman_series}
\caption[Raman spectra on \ce{Na_xWO3}]{Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
\label{fig:nawoxram}
\end{figure}
Based on the correlation of Raman spectra and crystallographic data of a variety of tungsten bronze, an empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths has been found as
\begin{equation}\label{eq:wobond}
\nu = 25823 \exp(-1.902\cdot R)
\end{equation}
where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm 0.034$ \si{\angstrom}. The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}. Multi-peak Lorentzian fitting is preformed to precisely determine the central maximum. Good fitting is obtained as shown in Fig.~\ref{fig:naworamfit}. The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} are then listed in Table~\ref{tab:nawobond}. The predicted \ce{W-O} bond lengths agree very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak probably is caused by \ce{Na-O} bond.
% Na5 raman fitting
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
\caption[Multi-peak Lorentzian fitting on \ce{Na5W_{14}O_{44}}]{Multi-peak Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}. The peaks sum height difference is caused by different baseline value adopted in each fitting.}
\label{fig:naworamfit}
\end{figure}

@@

Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na. The sodium concentration in 3N source was 20 ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively. To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N). These ultra-high purity W sources produced pure tungsten oxide deposition and no Na content was detected by EDX. These results verified the Na content was mainly from the 3N W powders. In the OT growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other sub-stoichiometric tungsten oxide vapors. The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item only small amount of the tungsten source was consumed during the growth; and
\item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source is difficult to probe. However, the evaporation rate of the Na content is expected to be high when heated at 1000 \si{\degreeCelsius}. This assumption is supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source. Put it in another way, this means that the majority of Na content was already evaporated in previous experiment. Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_edx_series.jpg}
\caption[Photograph of a series of specimens grown]{(a) Photograph of a series of specimens grown in the same reaction chamber with the increase of growth number showing different growth zones and corresponding morphology changes. (b) Change of Na/W ratios with the increase of growth number at different growth zones.}
\label{fig:nawoxser}
\end{figure}

As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth number. Three growth zones of nanowires can be identified on basis of the coverage and density of the nanowires, as delimited by the vertical guide line. The growth Zone I was located at high temperature end ranging from 660 to 520 \si{\degreeCelsius}, Zone II was from 520 to 470 \si{\degreeCelsius}, and Zone III from 470 to 420 \si{\degreeCelsius}. Detailed morphological changes are depicted in Fig.~\ref{fig:nawoxsemall}.
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_sem_series.jpg}
\caption[SEM images of morphology evolution]{SEM images of morphology evolution of the NWs at different growth zones showing morphology changes with the increase of growth number. The insets show detailed structures of the NWs.}
\label{fig:nawoxsemall}
\end{figure}
For the first growth (Fig.~\ref{fig:nawoxsemall}a-c) in a new clean reaction chamber, there were only a little nanowires scattered in Zone I (Fig.~\ref{fig:nawoxsemall}a), ultra-long nanowires were mostly found in Zone II with higher density and coverage (Fig.~\ref{fig:nawoxsemall}b), and in Zone III the coverage, density, and length of nanowires gradually reduced as the growth location moved downstream (Fig.~\ref{fig:nawoxsemall}c). With growth number increased to 3 (Fig.~\ref{fig:nawoxsemall}d-f) and 5 (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones. Zone I saw the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g. After the fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones. For Zones I and II, no significant morphology change was observed with further increase of the growth number up to 8. However, for Zone III the microplate structures (shown in inset of Fig.~\ref{fig:nawoxsemall}i) kept increasing significantly with the growth number. EDX study revealed the variation of Na concentration in the deposition with the growth number. Fig.~\ref{fig:nawoxser}b shows the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones. Generally, the Na/W ratios at all growth zones increased with the increase of growth number. The large fluctuation of Na/W ratio at Zone III was presumably due to the uneven distribution of Na content with different morphologies at Zone III.

@@

\subsection{Tungsten Oxides: Seeded Growth}\label{sec:sgfg}
